---
title: My Dynamic Report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
       background-image : url("https://img.freepik.com/premium-vector/seamless-pattern-with-cute-characters-takeaway-coffee-endless-background-retro-nostalgic-style_248911-2075.jpg?ga=GA1.1.657517678.1743494672&semt=ais_hybrid") ;
       font-size: 100%;
       background-size: contain ;
       color : white ;
       }

p {
    font-family : "Times New Roman" ; 
    background-color :#ffa4a4 ;
    font-weight : 400 ;
    font-size : 2em ;
    color : white ;
  }

h1{ 

   text-align: center ;
   background-color: #ffa4a4 ;
   font-weight: 700 ;
   font-size: 20vw;
   text : white ;
   border: 5px double white;
   
   }
   
h2{
    text-align: center ;
    background-color:#ffa4a4 ;
    font-size: 4em  ;
    text : white ; 
    border: 5px dotted white;
  }   
   
img {
  display: block;
  margin: auto;
  width: 50%;
    }
    



```

## The Drink Report: Beverage Purchase Insights

```{r}
library(tidyverse)
library(ggplot2)

logged_data <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRwbAiiwD9DprgTs_x6aT4Ucoc0wHOyEyD63iZKN-zaDZvA_9SNW5Dq1tk0RPsxNOpZYMZmLi9_fpkX/pub?output=csv"

latest_data <- read_csv(logged_data) %>%
     rename( weekday = 2,
            beverage_type = 3,
            location = 4,
            beverage_cost = 5,
            time_purchased = 6,
            amount_purchashed = 7,
            prefrance = 8)

```

```{r}
cost_mean <- mean(latest_data$beverage_cost)
print(cost_mean)
```

Upon observing the cost of beverages purchased, the average price per beverage bought is \$`r cost_mean`.

```{r}
soda_sum <- sum(latest_data$amount_purchashed[latest_data$beverage_type=="Soda"])

juice_sum <- sum(latest_data$amount_purchashed[latest_data$beverage_type=="Juice"])

hdrink_sum <- sum(latest_data$amount_purchashed[latest_data$beverage_type=="Hot Drink"])

water_sum <- sum(latest_data$amount_purchashed[latest_data$beverage_type=="Water"])

icedbev_sum <- sum(latest_data$amount_purchashed[latest_data$beverage_type=="Iced Beverage"])

print(soda_sum)
print(juice_sum)
print(hdrink_sum)
print(water_sum)
print(icedbev_sum)
```

Observing the amount of each beverage type purchased. I found that Sodas was purchased more, with the amount of `r soda_sum`. Comparing it to beverages such as water , with the amount of`r water_sum`, and iced beverages , with the amount of `r icedbev_sum`.

```{r}
ggplot(latest_data, aes(x = time_purchased , y = amount_purchashed, fill = time_purchased ,)) +
  geom_bar(stat = "identity") + labs(title = "The Amount of Beverages Bought in Different Time Intervals",
                                     x = "Time Intervals",
                                     y = "Amount Purchased")+
              theme_minimal(base_size = 7.5)

```


The bar graph above shows that the amount of beverages bought during different intervals throughout the day. I observed that there are more beverages bought in the afternoon than in the morning and evening. Due to the interval I associated with the afternoon , 12pm - 7pm , it's more likely to have more beverages purchased. As This interval includes times for lunch and dinner ( in some instances). 


```{r}
ggplot(latest_data, aes(x = beverage_type, y = prefrance , fill = beverage_type , color = )) +
  geom_bar(stat = "identity") + labs(title = "Prefrance for Different Types of Beverages",
                                         x = "Types of Beverages",
                                         y = "Prefrance")  
```

Observing the relationship between the different types of beverages and their preferences, its safe to say that Hot Drinks are preferred more than other types of beverages. 